\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-02 gwnnDraft02.tex
acknowledgements

\section*{Acknowledgement}
We thank Djuna Croon, Yang Bai and Yuhsin Tsai  for helpful discussions. P.A.S. and D.L. Both thank the 2018 Theoretical Advanced Study Institute in Elementary Particle Physics Program (TASI) for setting up a platform for discussion which seeded the genesis of this project. This work was supported by the Natural Sciences and Engineering Research Council of
Canada (NSERC). D.L. acknowledges support from the NSERC Postgraduate Scholarships-Doctoral Program (PGS D).

>>>>

\section*{Acknowledgement}
We thank Yang Bai, Djuna Croon, Kevin Earl, and Yuhsin Tsai for helpful discussions. P.A.S. and D.L. both thank the 2018 Theoretical Advanced Study Institute in Elementary Particle Physics Program (TASI) for setting up a platform for discussion which seeded the genesis of this project. This work was supported in part by the Natural Sciences and Engineering Research Council of
Canada (NSERC). D.L. acknowledges support from the NSERC Postgraduate Scholarships-Doctoral Program (PGS D).
